% \chapter*{References}
% \addcontentsline{toc}{chapter}{References} 

\begin{thebibliography}{9}
    \bibitem{REF5}
    Erin Schaffer
    \textit{What is Swift? Features, advantages, and syntax basics}
    \url{https://www.educative.io/blog/swift-programming}, 2021.

    \bibitem{REF6}
    Stefano Gasbarrino
    \textit{MVP: qué es el producto mínimo viable, cómo hacerlo y ejemplos}
    \url{https://blog.hubspot.es/sales/producto-minimo-viable#que-es}, 2024.

    \bibitem{REF7}
    \textit{LettuceMeet}
    \url{https://lettucemeet.com/}, 2024.

    \bibitem{REF8}
    \textit{Firebase Authentication}
    \url{https://firebase.google.com/docs/auth?hl=es-419}, 2023.

    \bibitem{REF9}
    \textit{App Store Review Guidelines}
    \url{https://developer.apple.com/app-store/review/guidelines/#5.1.1v}, 2024.

    \bibitem{REF10}
    \textit{OpenAI Moderation Endpoint Overview}
    \url{https://platform.openai.com/docs/guides/moderation/quickstart}, 2024.

    \bibitem{REF11}
    \textit{Meetup financials}
    \url{https://www.cbinsights.com/company/meetup/financials}, 2024.

    \bibitem{REF12}
    \textit{App Store Meetup Page}
    \url{https://apps.apple.com/us/app/meetup/id375990038}, 2024.

    \bibitem{REF13}
    \textit{Common Sense Census: Media Use by Tweens and Teens}
    \url{https://www.commonsensemedia.org/research/the-common-sense-census-media-use-by-tweens-and-teens-2021}, 2021.

    \bibitem{REF14}
    \textit{Number 10 in 2021: Can Married Men and Women Be Friends? Marriage, Friendship, and Loneliness}
    \url{https://ifstudies.org/blog/number-10-in-2021-can-married-men-and-women-be-friends-marriage-friendship-and-loneliness}, 2021.

    \bibitem{REF15}
    \textit{Soledad y aislamiento social vinculados a afecciones graves}
    \url{https://www.cdc.gov/aging/spanish/features/lonely-older-adults.html}, 2021.

    \bibitem{REF16}
    \textit{State of Friendships: The 2023 Meetup Measurement Report}
    \url{https://www.meetup.com/marketing-assets/PDF/Meetup+Trend+Report+v13.pdf}, 2023.

    \bibitem{REF17}
    \textit{React Native. Learn once, write anywhere}
    \url{https://reactnative.dev/}, 2024.

    \bibitem{REF18}
    \textit{Model-View-Controller (MVC) in iOS: A Modern Approach}
    \url{https://www.kodeco.com/1000705-model-view-controller-mvc-in-ios-a-modern-approach}, 2024.

\end{thebibliography}